A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-08 docs/methods/erosion_methods.tex
wrote first round of conclusion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}
We have developed a numerical framework for simulating two-dimensional
Stokesian erosion in a porous media.  By using a BIE formulation of the
fluid equations and a {\thL}, we achieve spectral accuracy in space and
second-order accuracy in time.  In addition, the non-negligible
interactions between different bodies are accurately resolved.

\todo[inline]{Here in revising}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}
We have combined two accurate and stable numerical methods to simulate
two-dimensional viscous erosion in a porous medium.  First, a BIE
formulation of the incompressible Stokes equations discretizes only the
boundary of the bodies and resolves their non-negligible interactions.
Second, the bodies are evolved with the so-called {\thL} variables to
avoid tangling and distortion of the mesh.  The resulting numerical
method is spectral in space, second-order in time, and is accelerated
with the fast multipole method.

Using slender body theory and flow past a wedge, the method is verified
against analytical results for the area, opening angle, and total drag
of a single eroding body.  Then, for multi-body erosion with a realistic
pressure drop boundary condition, we compute the area fraction, flow
rate, and total drag across a channel.  We observe that erosion leads to
channelization, and this reduces the resistance more than would be
expected if the area fraction were reduced by simply scaling down the
size of the bodies.  This indicates that the area fraction can not fully
characterize flow in eroding porous media since the interactions between
the bodies plays a role in the resistance.
